---
title: "Introduction to fcmTFN"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to fcmTFN}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(fcmfd)

set.seed(123)
```

# Introduction

The **fcmTFN** function extends the fuzzy c-means algorithm to handle ordinal data through a triangular fuzzy number (TFN) representation.

# Example Dataset

```{r}
data(sim_likert7)

head(sim_likert7)
```

# Running the Clustering Algorithm

```{r}
result <- fcmTFN(
  data = sim_likert7,
  option = "B",
  k_values = 2:6
)

summary(result)
```

# Cluster Assignment

```{r}
clusters <- cluster_assignment(result)

table(clusters)
```

# Cluster Quality

```{r}

```

# Prototype Interpretation

```{r}
prototype_results(result, format = "table")
```

```{r}
plot_prototypes(result, view = "global")
```

# Xie-Beni Index Visualization

```{r}
plot_xb(result)
```

# Conclusion

This vignette demonstrated the basic workflow for fuzzy clustering of ordinal data using the **fcmTFN** function from the fcmfd package.
